Expression QTL hotspot dissection with mediation analysis and pleiotropy testing

### 2019-07-29 analysis/paper/hotspot-one-chromosome.Rmd
fixed interval defining local traits

```{r}
local_annot2 <- local_annot %>%
  filter(middle <= hot_upper + 1, middle >= hot_lower - 1) %>% 
  # extend only 1 mb beyond hotspot end points (total interval length, for local traits, = 6 Mb)
  arrange(desc(lod))
```

>>>>

```{r}
local_annot2 <- local_annot %>%
  filter(middle <= hot_upper, middle >= hot_lower) %>% 
  arrange(desc(lod))
```
